Improving content discovery through combining linked data and data mining techniques

### 2016-05-06 report/chapters/02-background.tex
No more TODOs

\subsection{Enterprise Integration}
\subsection{Organisational Difficulties with Enterprise Integration}
\label{sec:ei-difficulties}
\subsection{Linked Enterprise Data}

>>>>

\subsection{Enterprise Integration}

The field of \emph{Enterprise Integration} is the study and application
of overcoming the fragmentation issues described in the previous
section. It is concerned with creating interconnectivity between
distinct systems, exchanging data between them and dealing with
distributed systems within the enterprise.\cite{vernadat2003enterprise}

\subsection{Organisational Difficulties with Enterprise Integration}
\label{sec:ei-difficulties}

Hohpe and Woolf\cite{hohpe2002enterprise} described a comprehensive
set of software design and architecture patterns that apply to this
field, but almost every pattern implies creating bespoke data flow
sofware for any given integration.

This means for every new system that is purchased or created, a
whole set of integration efforts are potentially initiated to move any
data into or out of that system.

A significant barrier to creating holistic views of all data
produced by an organisation is that each integration brings in a
vertical slice of all data required, but only for once source at a
time. If a hypothetical organisation has six content management
systems with actively-published content within them and each
integration effort takes one month, then it is a minimum of six
months before it can create something like a search feature over all
of that content.

\subsection{Linked Enterprise Data}

Allemang\cite{allemang2010semantic} proposed that a
\emph{linked data enterprise} can be truly agile by removing bottlenecks
created by enterprise integration efforts. There is an appealing
argument in using controlled vocabularies and efforts in linking
those vocabularies between systems to join up existing data silos
rather than trying to write integration layers to move data between
those silos.

A more detailed approach was outlined by Servant\cite{servant2008linking}
in how linking enterprise data might work with the view that it
could be adopted within Renault.

Real research in this area still seems sparse in the academic
literature, but there is arguably a case to be made for these
approaches for an organisations public-facing content given that is
already available on the public web.

The concept of linked enterprise data could encourage media
organisations to consider using linked data within all internal APIs
and data stores where possible such that reasoning across all that
information is more readily enabled. In this research, it is demonstrated
that we can get some value at least from the semantics available via
the content as it surfaces on the public World Wide Web, but this
value can be only increased if content producers improve the quality
of those semantics or linked data principles are used within internal
systems to reduce the need for bespoke enterprise integration effort.
